\begin{answer}\\
(a). We know that $K_1$ and $K_2$ are kernels. Therefore by definition they are positive semi definite.\\
Therefore $\forall z$, $z^TK_1z \geq 0$ and $\forall z, z^TK_2z \geq 0$\\
$\therefore z^TKz = z^TK_1z+z^TK_2z \geq 0$. Therefore $K$ is positive semidifinite. Therefore $K$ is a kernel.\\
\\
(b) From part (c) below we know that a positive number $\times$ a Kernel is a Kernel. So if we take $K2=aK_1 (a \geq 2)$ then $K=K_1-aK_1=(1-a)K_1$\\
But $1-a <0$ therefore using proof in part (d) we can say it is not a Kernel.\\
(c) $\forall z$, $z^TKz=z^TaK_1z=az^TK_1z=az^TK_1z$\\
Since $K_1$ is a Kernel, $z^TK_1z \geq 0$. Also since $a$ is a positive real number, $az^TK_1z \geq 0$ therefore it is a Kernel.\\
(d) $\forall z$, $z^TKz=z^T(-aK_1)z=-az^TK_1z$\\
Since $K_1$ is a Kernel, $z^TK_1z \geq 0$. Also since $a$ is a positive real number, $-az^TK_1z \leq 0$ therefore it is NOT a Kernel.\\
(e) We know that $K_1$ and $K_2$ are PSD\\
Therefore $z^TK_1z \geq 0$ and $z^TK_2z \geq 0$\\
Also $Z=zz^T$ is PSD. Let $U$ be orthogonal matrix. Then $UU^T=U^TU=I$\\
Then we know that $Z=U\Lambda U^T$\\
And $(U\Lambda U^T)^{-1}=(U^T)^{-1}(U \Lambda)^{-1}=U \Lambda^{-1} U^T$\\
$\therefore (zz^T)(zz^T)^{-1}(zz^T)^{-1}(zz^T)=I$\\
$\implies zz^T U \Lambda^{-1} U^T U \Lambda^{-1} U^T zz^T=I$\\
$\implies zz^T U \Lambda^{-1} \Lambda^{-1} U^T zz^T=I$\\
$\implies zz^T U \Lambda^{-2} U^T zz^T=I$\\
Let $x=U^Tz$. then $x^T=z^TU$. Therefore we can rewrite the above as\\
$z x^T \Lambda^{-2} x z^T=I$\\
Finally we have \\
$z^TKz=z^TK_1K_2z=z^TK_1IK_2z=z^TK_1 z x^T \Lambda^{-2} x z^TK_2z$\\
Since $\Lambda^{-2}$ is a diagonal matrix, it is positive semidefinite. Therefore $x^T \Lambda^{-2} x \geq 0$ and we already know that $z^TK_1 z \geq 0$ and $z^TK_2 z \geq 0$\\
Therefore the RHS is $\geq 0$\\
Therefore $z^TKz \geq 0$ and therefore it is a Kernel\\ 
(f) $K(x,y)=f(x)f(z)$.\\
Then $z^TKz=z_1^2f(x^{(1)})^2+2z_1z_2f(x^{(1)})f(x^{(2)})+z_2^2f(x^{(2)})^2+2z_2z_3f(x^{(2)})f(x^{(3)})+z_3^2f(x^{(3)})^2 \dots +z_3^2f(x^{(3)})^2$\\
$=(\sum_{i=1}^{m}z_i f(x^{(i)}))^2 \geq 0$\\
Therefore it is a kernel\\
(g) Since $K=K_3(\phi(x),\phi(z))$ it is Symmetric\\
Also $z^TKz=z^TK_3z \geq 0$ so K is a kernel.
(h) The polynomial can be written as $a_tK_3(x,z)^t+a_{t-1}K_3(x,z)^{t-1}+a_{t-2}K_3(x,z)^{t-2}+\dots+a_1K_3(x,z)+a_0$\\
From (e) the power of a Kernel is a Kernel\\
From (c) a positive number times a Kernel is a Kernel\\
Therefore each of the terms of the polynomial is a Kernel\\
Finally from (a) the sum of 2 kernels is a kernel. Therefore the polynomial is a kernel.
\end{answer}